A Survey of Current Exoskeletons and Their Control Architectures and Algorithms\\ (Draft 3.1)

### 2015-09-29 survey.tex
more updates

\title{A Survey of Exoskeleton Control Architectures and
Algorithms\\
(Draft 3.0)}

@@

@@

>>>>

\title{A Survey of Current Exoskeletons and Their Control Architectures and
Algorithms\\
(Draft 3.1)}

@@

This paper surveys the following exoskeletons in detail:
\begin{itemize}
\item
BLEEX: a ``minimal-sensing'' and aggressive model-based control design point.
\item
HAL: an EMG controlled exoskeleton.
\item
XoR: a hybrid Pneumatic/Electric-motor system.
\item
Body Extender: a fully actuated full body exoskeleton.
\item
IHMC MAE: an SEA-based torque controlled exoskeleton.
\item
MIT Exoskeleton: an attempt to take advantage of the passive dynamics
of walking.
\item
Roboknee: an example of a single-joint exoskeleton.
\end{itemize}

We then list other systems in a variety of categories.

\section{Introduction}

@@

\input{survey-atkeson}
